
\chapter*{Abstract}
\vspace{-40pt}
The ancestral concept of Cosmos is rediscovered through the idea of a Tachyonic
Grandcosmos Multibasis Computer, inversing the Anthropic Principle and reestablishing
the Laplace Determinism. The observed fine tuning between Physical dimensionless
parameters is interpreted as relations between optimal calculation basis, announcing a
dramatic progress in computer software. The three type of mathematical constants are
considered: Large, Intermediate and close to unity. The famous Large Number problem is
resolved by Eddington's statistical theory and the gravitational Hydrogen Molecule model,
leading to the visible Universe horizon radius $R = 13.812 Gly$. The extension of
the double cosmic correlation defines a Topological Axis using Euler-Neper constant e as
primary basis, confirming String Theory, Cartan-Bott periodicity and the 30 holic
dimensions corresponding to the simplest physical diophantine equation $T^2 = L^3 = M^5 =
N^30$ . The point $n = 30$ corresponds to the common time, about $10^58 s$, given by two
mandatory dimensional analysis, interpreted as the Supercycle period. The visible Universe
wavelength 'Topon' $2G ħ/ Rc^3 = 4 \cdot 10^-96 m$ corresponds to $n = 2e^e$ and enters the 1D mono-
radial holographic extension of the Bekenstein-Hawking Universe entropy, implying the
critical condition, and breaking the Planck wall by a factor $10^61$ . The monochrome
holographic extension leads to a Grandcosmos, larger than the visible Universe by the
same factor $10^61$ . This implies a tachyonic speed in the same ratio by respect to c, justifying
the Planck renormalisation of the Vacuum Energy, independently checked by the Casimir
effect. The couple Universe-Grandcosmos is confirmed by a dramatic geo-dimensional
analysis, where Length, Time and Mass are considered as unit vectors in a 3D Super-space.
A mater-antimater $10^104 Hz$ Oscillatory Bounce unifies standard Single Bang with steady-
state cosmology, but suppress Relativity in cosmology, reestablishing the Newton Absolute
Space-Time realized by the Microwave Cosmic Radiation. This new space-time structure are
tied to unexplained phenomena such as Kotov cycle, Tifft periodicity, Pioneer anomaly and
Arp observations. The Kotov period, omnipresent in astrophysics, is directly related with the
single-electron cosmology by a $10^-9$ relation. In addition to e, the Archimedes constant $\pi$
and the electric constant $a = 137.036$ appear as privileged calculation basis. The fusion
Mathematics-Physics is confirmed by 10 -9 precise relations with physical parameters
implying Eddington's 137 and Atiyah constant. The later enters the Topological axis in
liaison with the canonical Galaxy Group radius, the graviton mass and the Higgs Boson,
the later being associated to the string dimension $d = 496$. The dramatic connexion of
Atiyah constant with the Sternheimer scale factor confirms the fusion of Computation
Physics with Theoretical Biology. In particular, the Supercycle Period connects, through the
Monster group cardinal, with the Kotov period, itself tied to the well-defined DNA bi-codon
mass. The ratio between the Universe mass and the mass associated with the Kotov period,
identified with a photon mass, is close to the square of the Monster order. The ratio between
the Supercycle period and the Chronon quantum is close to the third power of the Monster
order, also close to $e^137e$ and $d^60$ . It is predicted that the future infra-red spatial telescopes
will find mature galaxies in the very far range, instead of a Dark Space, ruining definitely
the standard evolutionary cosmology, ill-founded on an imperfect Cosmological Principle.
