%%%%%%%%%%% Nomenclature for this chapter%%%%%%%%%%
\nomenclature{UOP}{University of Paris 11}
\chapter{Discussion}
\label{chap:chapter_4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Discussion}
\section {Discussion}

This article has answered several main problems : 

\begin {Enumerate}

\item[1.] Unification Gravitation-Quantum Physics,
by rehabilitating the forgotten Eddington's statistical theory, 
\item[2.] The real significance of Quantum
Physics, by assuming Physics is based on Arithmetics, 
\item[3.] The overall unification by showing that
cosmology is the basis of all science, 
\item[4.] The role of dimensionless parameters, by proving that they
are optimal basis of computation tied with the Holographic Principle and its arithmetic form, the
Holic Principle and 
\item[5.] The so-called Dark energy proportion 0.7, which is a false problem, since the
trivial ratio between gravitational energy and critical one of the observable universe is 3/10.
The high precision (ppb) of the relations shown in the present article prove that the traditional
scientific thinking is not at all baffled by the physical parameter values, meaning they are mere
mathematical constants. In the wonderful success of mathematical group formalism, it was
forgotten that the direct search for relations between measurement results has lead Dalton, Balmer,
Mendeleiev and Mendel to decisive discoveries, as recalled in the introduction. In this respect, the
high precision in the measurement of the Fermi constant, Muon mass, the background temperature
and the Kotov cosmic period must be saluted as decisive achievements. Now, we have also shown
[3] direct connexions between physical and biological parameters which have escaped researchers.
So, while the 'Anthropic Principle' states that Life implies a favored Cosmos among a Multiverse,
the `Inverse Anthropic Principle` [3] is more logical, stating that an all-deterministic single Cosmos
implies Life, in contradiction with the Darwin `accidental life` approach, a generally admitted so-
called `theory` which is contradicted by so many missing links [26].
Whilst the physicists community debates; the minority believes in a Single Final
Theory, whereas a vast majority have given-up their believes towards an `Anthropic Principle` primacy, the Multiverse conundrum. The present article settles the
arguments in favor of a single steady-state cosmos.
Another type of separation exists, but with not any debate: only a small minority think Physics
and Mathematics are unified, while a large majority separates the two domains (so separating also
Biology). The present article shows that the former are right: physical constants are mathematical
constants, so the present-day mathematics are still in enfancy, not realizing that the discovery of
sporadic groups is a crucial discovery for physics. In particular, we have clearly shown that
Grandcosmos is a computer which uses optimal physico-mathematical constants as calculation basis
and that they are present in DNA characteristics [3]. The present article show definitely the liaisons
with π, e and γ, and rehabilitates String theories, also abandoned by a majority [27].
There is also the Determinism separation, a majority believing seriously that 'God plays dices',in contradiction with our Cosmic Computing Principle. The c-free analysis gives simply and
directly the Large time periodicity of an all-deterministic Grandcosmos, as it gives in an elementary
calculation the visible Universe horizon radius, in a formula which was present for a century in
astrophysics text-books: the limit of a star radius when the number of atoms reduce to unity [3].
This is tied to the application of the exclusion principle that Eddington dared to apply in cosmology.
For this reason he was declared 'crakpot' and his theory discarded by a majority. The same rejection
seems to apply now to Atiyah's last work. Fortunately, the large theoretical advance of Eddington is
now recognized [28][29], but without mentioning a crucial point: he predicted the tau fermion with
a right order of mass, 30 years before its surprising discovery, calling it Heavy Mesotron [1].
It seems that the pre-scientific role of chance is a common point between three misleading views
in present mainstream thinking. Firstly, in biology, the assimilation of Darwin vague arguments
with a scientific theory. Secondly, in quantum physics, the so-called 'incertitude relations', which are
only manifestations of the general (Field and flickering Matter) wave propagation, through Fourier
transform properties. Thirdly, in cosmology, the recourse to the Multiverse conundrum.
\end {Enumerate}
