%%%%%%%%%%% nomenclature %%%%%%%%%%
\nomenclature{UOP}{}
%\nomenclature{IIT}{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Introduction}

Deterministic Computation and Hierarchy Principle:
\begin{center}
It was observed that the physical constants are tightly contrived, but only three dimensionless
parameters: a, p, and a G, are sufficient to explain the main structures of the world [1]. Two of them
are precisely measured: the electric constant $a = 137.035999139(31)$, measured with 0.23 ppb
precision and the proton-electron mass ration $p = 1836.15267245(75)$, known with 0.41 ppb
precision. By contrast, the gravitational coupling constant a G was neither well defined nor
measured, due to the relatively large imprecision on G measurement ($10^-4$ ).
One can read [1]: 'For example, the size of a planet is the geometric mean of the size of the
Universe and the size of an atom; the mass of man is the geometric mean of the mass of a planet
and the mass of a proton. Such relationships, as well as the basic dependences on a and a G from
which they derive, might be regarded as coincidences if one does not appreciate that they can be
deduced from known physical theory, with the exception of the Universe, which cannot be explained
directly from kwown physics.... This line of arguments, which is discussed later, appeals to the
**anthropic principle**.'
The existence of relations that are not explained by known physical theories, is called 'fine
tuning' phenomena. But as soon as it involves the observable Universe radius, it signals the
existence of a more fundamental theory that must take into account the ancestral Cosmos concept,
which, as Eddington prophetised [2], must be permanent [3].
But, as about 30 dimensionless parameters appear as 'free parameters' in the Particle standard
model, a large majority of theorists believe rather they are due to chance, leading to a separation
between Physics and Mathematics, not to speak of Biology. Through a so-called Anthropic
Principle, a majority believe in the Multiverse conundrum, a multiplicity of sterile Universe [1].
The present article shows that Physics is a part of mathematics, refuting the Multiverse
Hypothesis by precise fine-tuning between main physical and biological parameters, involving
main mathematical constants: $\pi, e and \gamma $. Also, these relations confirm the Super-string Theory and
rehabilitates the tachyonic Bosonic String Theory.
A magic of physics is the energy conservation. Theorists associate it with time uniformity, but a
more logical explication is that cosmos is a computer, so Intelligent Life receive a justification: to
help the Cosmos computation. This Inverted Anthropic Principle answers the first of all questions :
why do we ask questions ? We proposed that the parameters are optimal basis in a deterministic
Computing Cosmos, and they appear indeed in DNA characteristics, and three-point temperatures of
Mammals and main molecules [3] (this ref contains well-known ref. not recalled here)
This reestablishes the Laplace determinism, rejecting the Copenhague stastitical interpretation of
quantum mechanics, involving non-local hidden variables, which identify with the Cosmos.
The fact that three parameters, out of about 30, are so clearly emerging means that Physics, and
more generally Science, is hierarchic: one can progress in science without knowing the details of
the underlying fundamental theory.
So, when Dalton found whole numbers in chemical reactions, he was prefiguring the atoms and
Chemistry. The same for Balmer, spectral lines and wave mechanics. The same for Mandeleiev,
atomic masses and nuclear physics. Also, when Mandel found whole numbers in Biology, he was
prefiguring genetics. In the same manner, this article prefigures the fundamental theory which must
be based on arithmetics, indeed a characteristic of deterministic computation.
This article is separated in 3 sections, corresponding to 3 classes of mathematical constants.
The first section explains why, in the Computation Hypothesis, large numbers are necessary, so
justifying at last the Cosmos vastness. In particular, the most famous prime number of History $2^127 -
1$, and the Eddington's Large number $N_Ed = 136 \cdot {2^256}$ are empathized. The second section will study
the role of intermediate mathematical constants such as the Eddington's constant 137. The third
Section involves mathematical constants, such as $\pi and \gamma$. By contrast, the optimal computation
basis e is used all along, in particular as the primary basis of the Topological Axis (the secondary
basis being 2, the simplest of all)..
\end{center}

\iftoggle{edit-mode}{\hspace{0pt}\marginpar{Recognition-based segmentation}}{}

